\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-08-16 onebit_full.tex
small changes
changed h to h_n in proof of Thm. 12

We have the following results:
\begin{thm} \label{thm:sgd}
Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
\begin{enumerate}
\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
\begin{equation} \label{eq:conditions1}
\begin{cases}
\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
\mathrm{for~some~}0< \lambda \leq 1
\end{cases}
\end{equation}
(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
\[
\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
\]
%
%
\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with finite Fisher information for location
\[
I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
\]
%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
Then for any bounded, symmetric, and quasi-convex function $L$, 
\begin{align} 
& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
\\
& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
\end{align}
where $Z \sim \Ncal(0,1)$. 
%
%
\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
\begin{equation} \label{eq:conditions2}
\begin{cases}
\gamma_n = o(n^{-2/3}), &  \\
\sum_{n=1}^\infty \gamma_n = \infty.  & \\
\end{cases}
\end{equation}
(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
\[
 \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
\]
\end{enumerate}
\end{thm}

@@

\subsubsection*{Proof of (ii)}
We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates. Then 
\begin{align}
\label{eq:sgd_part2}
\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
\end{align}
under $\Prob_{\theta,n}$. Under the assumption that $f(x)$ is continuously differentiable with finite Fisher information for location, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm. 7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
\[
\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
\]
where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
 The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
$ is bounded, and hence 
\[
\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
\]

Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence the proof of (ii) follows once we establish the regularity of $\bar{\theta}_n$. \\

%Any estimator satisfying \eqref{eq:sgd_part2} also satisfies \eqref{eq:attaining_LAM} \cite[P. 157]{ibragimov2013statistical}.

The proof of the regularity of $\bar{\theta}_n$ requires the following refinement of Theorem~\ref{thm:polyak_juditsky}.
\begin{thm} \label{thm:normal_expansion}
Set $\Delta_i = \theta_i - \theta$ and
$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
\begin{equation}
\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
\label{eq:PJ_additional_cond}. 
\end{equation}
Then:
\begin{itemize}
\item[(i)] \begin{equation}
\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
\end{equation}
where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
\[
I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
\]
then
\[
\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-1}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
\]
under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h/\sqrt{n}}$ with density $f^n(x-h/\sqrt{n})$.
\end{itemize}
\end{thm}
The proof of Theorem~\ref{thm:normal_expansion} is given in Subsection~\ref{proof:thm:normal_expansion} below. \\

We have, 
\begin{align*}
& %\varphi(Z_1) - \varphi(x+Z_1) = 
\sgn(Z_1) - \sgn(x + Z_1) \\
& = \begin{cases}
2 & Z_1 > 0,\, x+Z_1<0, \\
-2 & Z_1 <0, \, x+Z_1>0, \\
0 & \text{otherwise}. 
\end{cases}
\end{align*}
It follows that
\begin{align*}
\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
\end{align*}
hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
\[
\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = 2f(0) = \psi'(0). 
\]
Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.

@@

\subsection{Proof of Theorem~\ref{thm:normal_expansion}
\label{proof:thm:normal_expansion}
}
\subsubsection*{Proof of (i)}
The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
\label{lem:Polyak_expansion}
Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
\[
\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
\]
Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} hold. Then 
\begin{equation}
\label{eq:Polyak_expansion}
\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
\end{equation}
where $\alpha_n$, and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
\[
\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
\]
\end{lem}

@@

We separate the proof of part (i) into two steps.
\subsubsection*{Step I}
The expansion \eqref{eq:normal_expansion_lem} holds for the process  ${\bar{\Delta}^1_i}$ defined as follows:
\begin{align} \label{eq:Polyak_expansion_lem1_alg}
& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
 \delta_0^1 = \Delta_0\\
& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
\end{align}

In order to show this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$. The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance. In addition, 
\begin{align*}
& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
\end{align*}
We obtain
\begin{equation}
\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
\end{equation}

@@

\subsubsection*{Part (ii)}
Use \eqref{eq:normal_expansion_lem} to write
\[
\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
\]
where
\[
G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
\]
From \cite[Exm. 7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$. This fact implies the following expansion \cite[Thm. 7.2]{van2000asymptotic}:
\begin{align}
\label{eq:PJ_LAN}
& \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
\end{align}
where 
\[
J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
\]
We have
\begin{align*}
& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
\end{align*}
Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
\[
\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
\end{pmatrix}  \right)
\]
Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
\[
\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
\]

>>>>

We have the following results:
\begin{thm} \label{thm:sgd}
Consider the sequence $\left\{\bar{\theta}_n \right\}_{n\in \mathbb N}$ defined by \eqref{eq:sgd_est}. 
\begin{enumerate}
\item[(i)] Assume that $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
\begin{equation} \label{eq:conditions1}
\begin{cases}
\frac{\gamma_n - \gamma_{n+1}}{\gamma_n} = o(\gamma_n), &  \\
\sum_{n=1}^\infty \frac{\gamma_n^{(1+\lambda)/2}} {\sqrt{n}} < \infty, & 
\mathrm{for~some~}0< \lambda \leq 1
\end{cases}
\end{equation}
(e.g., $\gamma_n = n^{-\beta}$ for $\beta \in (0,1)$). Then
\[
\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left(0,\frac{1}{\eta(0)}\right).
\]
%
%
\item [(ii)] Assume in addition that $f(x)$ is continuously differentiable with a finite location Fisher information, namely
\[
I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)}  \right)^2 f(x) dx < \infty.
\]
%(or that $f(x-\theta)$ is differentiable in quadratic mean).  
Then for any bounded, symmetric, and quasi-convex function $L$, 
\begin{align} 
& \liminf_{c \to \infty} \liminf_{n \to \infty} \sup_{\tau\,:\,|\theta-\tau| \leq \frac{c}{\sqrt{n} }}  \mathbb E \left[ L\left( \sqrt{n}(\bar{\theta}_{n} - \tau) \right) \right] \nonumber 
\\
& \qquad \qquad \qquad \qquad = \mathbb E \left[ L (Z/\sqrt{\eta(0)}) \right], \label{eq:attaining_LAM}
\end{align}
where $Z \sim \Ncal(0,1)$. 
%
%
\item[(iii)] Assume that, in addition to \eqref{eq:conditions1}, $\left\{ \gamma_n \right\}_{n\in \mathbb N}$ satisfies
\begin{equation} \label{eq:conditions2}
\begin{cases}
\gamma_n = o(n^{-2/3}), &  \\
\sum_{n=1}^\infty \gamma_n = \infty.  & \\
\end{cases}
\end{equation}
(e.g., $\gamma_n = n^{-\beta}$ with $\beta \in (2/3,1)$). Then
\[
 \ex{\left( \bar{\theta}_n - \theta \right)^2} = \frac{1}{n\eta(0)} + o(n^{-1}). 
\]
\end{enumerate}
\end{thm}

@@

\subsubsection*{Proof of (ii)}
We first show that the estimator $\bar{\theta}_n$ is regular in the following sense: For $\theta \in \Theta$, $h\in \mathbb R$ and $n$ large enough such that $\theta+h/\sqrt{n} \in \Theta$, let $\Prob_{\theta,n}$ be a product probability measure on $\mathbb R^n$ with density $f(x-\theta - h/\sqrt{n})$ in each of its $n$ coordinates. Then 
\begin{align}
\label{eq:sgd_part2}
\sqrt{n}\left( \bar{\theta}_n - \theta\right) \overset{d}{\to} \Ncal\left( h,\frac{1}{\eta(0)}\right),
\end{align}
under $\Prob_{\theta,n}$. Under the assumption that $f(x)$ is continuously differentiable with a finite location Fisher information, the model $\{Z_n+ \theta\}_{n \in \mathbb N}$ is differentiable in quadratic mean \cite[Exm. 7.8]{van2000asymptotic} and hence local asymptotically normal (LAN) in the sense that
\[
\log \left(\frac{\Prob_{\theta,n}(X^n)}{\Prob_{\theta} (X^n) }\right) = h \eta^{-1/2}(0) Z - \frac{1}{2} h^2 \eta^{-1}(0)  + o_{p,n}(1),
\]
where $Z\sim \Ncal(0,1)$ and $o_{p,n}(1) \to 0$ as $n\to \infty$ under $\Prob_{\theta}$. 
 The random variable $L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)
$ is bounded, and hence 
\[
\ex{ L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)} \to \ex{L\left(\sqrt{n} \left(\bar{\theta}_n - \tau \right) \right)}
\]
Any regular estimators in a LAN model satisfies \eqref{eq:attaining_LAM} \cite{beran1995role}, hence in order to prove (ii) it is left to show that $\bar{\theta}_n$ is regular. For this purpose, 
we use the following refinement of Theorem~\ref{thm:polyak_juditsky}, proof of which is given in Subsection~\ref{proof:thm:normal_expansion} below.
%
\begin{thm} \label{thm:normal_expansion}
Set $\Delta_i = \theta_i - \theta$ and
$\bar{\Delta_i} = \frac{1}{n} \sum_{i=1}^n \Delta_i$. Assume that, in addition to Assumptions (i)-(iv) of Theorem~\ref{thm:polyak_juditsky}, there exists $K_1$ and $\lambda>0$ such that
\begin{equation}
\ex{\left| \varphi(Z_1) - \varphi(x+Z_1)  \right|} \leq K_1 |x|^{1+\lambda}
\label{eq:PJ_additional_cond}. 
\end{equation}
Then:
\begin{itemize}
\item[(i)] \begin{equation}
\sqrt{n} \bar{\Delta}_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1). \label{eq:normal_expansion_lem}
\end{equation}
where $o_{p,n}(1)$ converges in probability to $0$ as $n\to \infty$.
\item[(ii)] If $Z_1$ has continuously differentiable density $f(x)$ with finite location Fisher information 
\[
I_\theta = \int_{\mathbb R} \left( \frac{f'(x)}{f(x)} \right)^2 f(x) dx,
\]
then for any converging sequence $h_n \to h$,
\[
\sqrt{n} \left( \bar{\Delta}_n \right) \overset{d}{\to} \Ncal\left( \frac{-h}{\psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx  , \frac{\chi(0)}{\psi'^2(0)} \right)
\]
under the local alternative $Z_1,\ldots,Z_n \sim \Prob^n_{h_n/\sqrt{n}}$ with density $\prod_{i=1}^n f(x_i-h_n/\sqrt{n})$.
\end{itemize}
\end{thm}
We now use this theorem to show regularity of $\bar{\theta}_n$. We have, 
\begin{align*}
& %\varphi(Z_1) - \varphi(x+Z_1) = 
\sgn(Z_1) - \sgn(x + Z_1) \\
& = \begin{cases}
2 & Z_1 > 0,\, x+Z_1<0, \\
-2 & Z_1 <0, \, x+Z_1>0, \\
0 & \text{otherwise}. 
\end{cases}
\end{align*}
It follows that
\begin{align*}
\ex{ \left| \varphi(Z_1) - \varphi(x+Z_1) \right| }  \leq \Prob\left( |Z_1| < x  \right) \leq f(0) |x|, 
\end{align*}
hence condition \eqref{eq:PJ_additional_cond} is fulfilled. In addition, by anti symmetry of $f'(x)$ around $x=0$, 
\[
\int_{\mathbb R} \varphi(x) f'(x) dx = \int_{\mathbb R} \sgn(x) f'(x) dx = 2\int_0^\infty f'(x) dx = -2f(0) = -\psi'(0). 
\]
Theorem~\ref{thm:normal_expansion}, applied to the setting of Theorem~\ref{thm:sgd}, implies \eqref{eq:sgd_part2}.

@@

\subsection{Proof of Theorem~\ref{thm:normal_expansion}
\label{proof:thm:normal_expansion}
}
\subsubsection*{Proof of (i)}
The proof of part (i) of Theorem~\ref{thm:normal_expansion} requires the following two additional results from \cite{polyak1992acceleration}:
\begin{lem}{\cite[Lem. 2]{polyak1992acceleration}}
\label{lem:Polyak_expansion}
Consider the process $\{\Delta_i^1 \}_{i=0}^\infty$ defined by
\[
\Delta^1_i = \Delta^1_{i-1} - \gamma_i (A \Delta_{i-1}+ \xi_i),\quad i=1,2\ldots.
\]
Assume that $A>0$ and condition (ii) of Theorem~\ref{thm:polyak_juditsky} holds. Then 
\begin{equation}
\label{eq:Polyak_expansion}
\sqrt{n} \bar{\Delta}_n^1 = \frac{1}{\sqrt{n}}\sum_{i=0}^{n-1} \Delta_i^1 = \frac{\alpha_n \Delta_0^1}{\sqrt{n} \gamma_0}  + \frac{1}{\sqrt{n} A} \sum_{i=1}^{n-1} \xi_i + \frac{1}{\sqrt{n}}\sum_{i=1}^{n-1} w_i^n \xi_i,
\end{equation}
where $\alpha_n$ and $w_i^n$ are real numbers such that $|\alpha_n| \leq K$ and $|w_i^n|\leq K$ for some $K< \infty$, and 
\[
\lim_{n\to \infty} \frac{1}{n} \sum_{i=1}^{n-1} |w_i^n| = 0. 
\]
\end{lem}

@@

We separate the proof of part (i) into two steps.
\subsubsection*{Step I}
The expansion \eqref{eq:normal_expansion_lem} holds for the process  $\{\bar{\Delta}^1_i\}_{i=1}^\infty$ defined as follows:
\begin{align} \label{eq:Polyak_expansion_lem1_alg}
& \Delta_i^1  = \Delta_{i-1}^1 - \gamma_i \psi'(0) \Delta_{i-1}^1 - \gamma_i \varphi(Z_i), \qquad
 \delta_0^1 = \Delta_0\\
& \bar{\Delta}^1_i = \frac{1}{n}\sum_{i=0}^{n-1} \Delta^1_i.
\end{align}

In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$. The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance. In addition, 
\begin{align*}
& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
\end{align*}
We obtain
\begin{equation}
\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
\end{equation}

@@

\subsubsection*{Part (ii)}
Use \eqref{eq:normal_expansion_lem} to write
\[
\sqrt{n} \bar{\Delta}_n = G_n + o_{p,n}(1),
\]
where
\[
G_n \triangleq -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n} \varphi(Z_i). 
\]
From \cite[Exm. 7.8]{van2000asymptotic}, the location model $f(x-\theta)$ with continuously differentiable $f(x)$ is differentiable in quadratic mean with the score function $-f'(x-\theta)/f(x-\theta)$. This fact implies the following expansion \cite[Thm. 7.2]{van2000asymptotic}:
\begin{align}
\label{eq:PJ_LAN}
& \log \frac{\Prob^n_{h_n/\sqrt{n}}}{\Prob^n_0} (Z_1,\ldots,Z_n) =  \log \prod_{i=1}^{n} \frac{f(Z_i-h_n/\sqrt{n})}  {f(X_i-\theta)} = h J_n - \frac{1}{2}h^2 I_{\theta} + o_{p,n}(1),
\end{align}
for any converging sequence $h_n \to h$, 
where 
\[
J_n \triangleq -\frac{1}{\sqrt{n}} \sum_{i=1}^n \frac{f'(Z_i)}{f(Z_i)} .
\]
We have
\begin{align*}
& \ex{ G_n J_n} = \frac{1}{\psi'(0)}\frac{1}{n} \sum_{i=1}^n \ex{ \varphi(Z_i) \frac{f'(Z_i)}{f(Z_i)} }  \\
& = \frac{1}{ \psi'(0)} \ex{ \varphi(Z_1) \frac{f'(Z_1)}{f(Z_1)}} =  \frac{1}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx , 
\end{align*}
Since both $\sqrt{n}G_n$ and $\sqrt{n}J_n$ are the sum of $n$ i.i.d. random variables with zero mean and finite variance, we obtain, from the central limit theorem and Slutsky's theorem, that
\[
\left(\sqrt{n} \bar{\Delta}_n, \log \frac{\Prob^n_{h/\sqrt{n}}}{\Prob^n_0} \right) \overset{d}{\to} \Ncal \left( \left(0,-\frac{h^2}{2} I_\theta \right),  \begin{pmatrix}
\frac{\chi(0)}{\psi'^2(0)} & \frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx \\
\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx & h^2 I_\theta 
\end{pmatrix}  \right)
\]
Le Cam's third lemma \cite[Exm. 6.7]{van2000asymptotic} implies that under $\Prob^n_{h/\sqrt{n}}$, 
\[
\sqrt{n}\bar{\Delta}_n \overset{d}{\to} \Ncal\left(\frac{-h}{ \psi'(0)} \int_{\mathbb R} \varphi(x) f'(x) dx,  \frac{\chi(0)}{\psi'^2(0)} \right).
\]
